Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-18 CAV2018/paper.tex
additional explanation regarding the optimization step in sec 7

We enhance the standard CEGIS architecture with an abstraction-refinement
approach and with optimization.  We call the resulting new technique
\emph{CEGIS-OR} (CEGIS with Optimization and Refinement).  By using
abstraction refinement, CEGIS-OR addresses the scalability issues inherent
in program synthesis and enables us to handle complex systems, which we
coarsely abstract and only refine on demand -- refinements are triggered by
counterexamples returned by the verification phase.
%
%potentially coarse abstractions of the given model that are only
%refined on demand.
%
Since the use of coarse abstractions may result in low-quality candidate
solutions (i.e.  candidates that fail the specification on a very large
number of inputs), after each synthesis phase we use optimization techniques
to improve the produced candidates.  In particular, our optimization
procedure aims at reducing the size of the reach space of the closed loop
system, while maintaining other dynamical properties (safety, stability, and
response time).

@@

The main advantage of the new CEGIS-OR is twofold:
\begin{itemize}
\item[1.] We start with coarse abstractions that get
  refined into more complex ones as the procedure progresses. Thus, solutions
  that do not require a high level of precision are obtained faster. 
\item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
  by optimizing the candidate solution in each iteration of the CEGIS loop
  we obtain better candidates that are more likely to meet the
  specification or produce high quality counterexamples in the
  {\sc verify} phase.
  This has the potential to reduce
  the overall number of iterations of the CEGIS loop required to obtain a complete solution.
\end{itemize}

>>>>

We enhance the standard CEGIS architecture with an abstraction-refinement
approach and with optimization.  We call the resulting new technique
CEGIS-OR (CEGIS with Optimization and Refinement).  By using
abstraction refinement, CEGIS-OR addresses the scalability issues inherent
in program synthesis and enables us to handle complex systems, which we
coarsely abstract and only refine on demand -- refinements are triggered by
counterexamples returned by the verification phase.
%
%potentially coarse abstractions of the given model that are only
%refined on demand.
%
Since the use of coarse abstractions may result in low-quality candidate
solutions (i.e.  candidates that fail the specification on a very large
number of inputs), after each synthesis phase we use optimization techniques
to improve the produced candidates.  In particular, our optimization
procedure aims at reducing the size of the reach space of the closed loop
system, while maintaining other dynamical properties (safety, stability, and
response time).

@@

The main advantage of the new CEGIS-OR is twofold:
\begin{itemize}
\item[1.] We start with coarse abstractions that get refined into more
  complex ones as the procedure progresses. Thus, solutions that do
  not require a high level of precision are obtained faster.  Note
  that the optimization step plays an important role here given that,
  in its absence, the use of coarse abstractions often results in
  low-quality candidate solutions (i.e., candidates that fail the
  specification on a very large number of inputs) and, consequently,
  there are very few solutions obtained at such low levels of
  precision.
\item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
  by optimizing the candidate solution in each iteration of the CEGIS loop
  we obtain better candidates that are more likely to meet the
  specification or produce high quality counterexamples in the
  {\sc verify} phase.
  This has the potential to reduce
  the overall number of iterations of the CEGIS loop required to obtain a complete solution.
\end{itemize}
